Paper figures

### 2021-04-05 notebooks/paper_plots_1213_pcc_only.Rmd
text size changes for fig5

```{r}
library(reticulate)
# use_python("/home/oma21/miniconda3/envs/enm/bin/python")
use_condaenv("enm")
setwd("../")
source("src/R/plot_density_prs.R")
```

@@

```{r}
library(tidyverse)
library(cowplot)
library(ggpubr)
library(ggsignif)

@@

```{python}
from matplotlib.lines import Line2D
pos = e_pcc.graph_gc.nodes('pos')
fig, ax = plt.subplots(figsize=(12,12))
legend_elements = [    ]
e_pcc.plot_network_spring(ax=ax,
                          node_size=1,
                          node_color='black',
 #                        node_size = [100 if i in sensors_pcc.orf_name.values or i in effector_pcc.orf_name.values else 1 for i in e_pcc.nodes],
                         #node_color = ['red' if i in sensors_pcc.orf_name.values else 'blue' if i in effector_pcc.orf_name.values else 'black' for i in e_pcc.nodes],
                         edge_color='black')
#                         node_shape=['^' if i in sensors_pcc.orf_name.values else 'v' if i in effector_pcc.orf_name.values else 'o' for i in e_pcc.nodes])
nx.draw_networkx_nodes(e_pcc.graph_gc, nodelist=sensors_pcc.orf_name.values, node_size=200, pos=pos,
                          node_color='black',
                          node_shape='^',edgecolors='black',
                          linewidths=1)
legend_elements.append(
    Line2D([0], [0], marker='^', color='black', label=f'Sensors (No GO enrichment)',
                          markerfacecolor=sensor_colors[0], markersize=12, linestyle="None")
)
for itr, i in enumerate(sensor_order):
    #print(i, effector_colors[itr])

    orf_names_to_plot = sensors_pcc.loc[sensors_pcc.go_group==i, 'orf_name'].tolist()
    nx.draw_networkx_nodes(e_pcc.graph_gc, nodelist=orf_names_to_plot, node_size=200, pos=pos,
                          node_color=sensor_colors[itr],
                          node_shape='^',edgecolors='black',
                          linewidths=1)
    legend_elements.append(
        Line2D([0], [0], marker='^', color='black', label=f'Sensors ({i})',
                              markerfacecolor=sensor_colors[itr], markersize=16, linestyle="None")
    )
nx.draw_networkx_edges(nx.induced_subgraph(e_pcc.graph_gc, sensors_pcc.orf_name.tolist()), ax=ax , pos=pos, edge_color='red', alpha=0.5)
ax.set_facecolor('white')
legend_elements.extend(
    [Line2D([0], [0], marker='o', color='black', label='Genes',
                              markerfacecolor='black', markersize=4, linestyle="None"),
#                    Line2D([0], [0], marker='o', color='black', label='Effectors',
#                               markerfacecolor='black', markersize=10, linestyle="None"),
#                    Line2D([0], [0], marker='^', color='black', label='Sensors',
#                               markerfacecolor='black', markersize=10, linestyle="None"),
                       Line2D([0], [0], marker='o', color='black', label= 'High functional similarity',
                              markerfacecolor='black', markersize=0, linestyle="-"),
                   Line2D([0], [0], marker='o', color='red', label= 'Sensor-Sensor edges',
                              markerfacecolor='#018571', markersize=0, linestyle="-")
])
lgd = ax.legend(handles=legend_elements, fontsize=22,loc='center left', bbox_to_anchor=(1.1, 0.5))
plt.savefig('reports/figures/CSHL_plots_022621/tmp_nwsens.png',bbox_inches='tight')
#plt.savefig('tmp_nw.png',bbox_inches='tight')
```

@@

eff_deg_comp <- ggplot(effector_pcc %>% right_join(py$e_pcc$df)%>% mutate(go_group = factor(replace_na(as.character(go_group),"Others")),go_group=fct_reorder(go_group, eff),go_group=fct_relevel(go_group,'Others',after=Inf)), 
                       aes(x = go_group, y = deg, fill = go_group)) +
  geom_boxplot(outlier.shape = NA) +
  scale_fill_manual(
    values = c(effector_colors,'black'),
    labels = c("Chromosome\nSegragetion", "Golgi vesicle\nTransport", "Respiratory complex\nassembly",'Non-effector genes')
  ) +
  xlab("") +
  ylab("Degree") +
  theme_bw() +
  geom_signif(
    comparisons = list(c("golgi", "chromatin"), c("golgi", "mito"), c("mito", "chromatin")),
    annotation = c("**", "***", "ns"),
    y_position = c(115, 120, 130)
  ) +
  theme(axis.text.x = element_blank(), legend.title = element_blank(), legend.text = element_text(margin = margin(t = 10, b = 10))) # , legend.spacing.y = unit(2,'in'))+
ggsave("reports/figures/CSHL_plots_022621/tmp_eff_deg_nolegend.png", plot = eff_deg_comp+theme(legend.position='none'),width=4,height=4)

eff_eff_comp <- ggplot(effector_pcc %>% mutate(go_group = fct_reorder(go_group, eff)) %>%
  mutate(eff_norm = eff / 5183), aes(x = go_group, y = eff_norm, fill = go_group)) +
  geom_boxplot() +
  # scale_x_discrete(labels=c('Chromosome\nSegragetion','Golgi vesicle\nTransport','Respiratory complex\nassembly'))+
  xlab("") +
  ggpubr::stat_compare_means(method = "kruskal.test") +
  scale_fill_manual(values = effector_colors) +
  ylab("Effectiveness") +
  theme_bw() +
  theme(axis.text.x = element_blank(), legend.title = element_blank())
ggsave("reports/figures/CSHL_plots_022621/tmp_eff_eff.png", plot = eff_eff_comp+theme(legend.position='none'),width=4,height=4)

sens_deg_comp <- ggplot(sensors_pcc %>% drop_na() %>% right_join(py$e_pcc$df)%>% mutate(go_group = factor(replace_na(as.character(go_group),"Non-sensor genes")),go_group=fct_reorder(go_group, sens),go_group=fct_relevel(go_group,'Non-sensor genes',after=Inf)), aes(x = go_group, y = deg, fill = go_group)) +
  geom_boxplot(
    outlier.shape=NA) +
  #    scale_x_discrete(labels=c('Chromosome\nSegragetion','Golgi vesicle\nTransport','Respiratory complex\nassembly'))+
  xlab("") +
  ylab("Degree") +
  scale_fill_manual(values = c(sensor_colors[1:6],'black')) +
  ggpubr::stat_compare_means(method = "kruskal.test", label.x.npc = .3) +
  theme_bw() +
  theme(
    axis.text.x = element_blank(), legend.title = element_blank(),
    legend.text = element_text(margin = margin(t = 10, b = 10))
  )+scale_y_log10()
  ggsave('reports/figures/CSHL_plots_022621/sens_deg_withlegend.png', plot=sens_deg_comp,width=4,height=4)

@@

sens_sens_comp <- ggplot(sensors_pcc %>% drop_na() %>% mutate(go_group = fct_reorder(go_group, sens)) %>%
  mutate(sens_norm = sens / 5183), aes(x = go_group, y = sens_norm, fill = go_group)) +
  geom_boxplot() +
  geom_signif(
    comparisons = list(
      c("hexose metabolic\nprocess", "phenylalanine\ntransport"), c("tricarboxylic\nacid cycle", "phenylalanine\ntransport"),
      c("phenylalanine\ntransport", "protein folding")
    ),
    annotation = c("**", "**", "*"), y_position = c(0.007, 0.0075, 0.008)
  ) +
  #    scale_x_discrete(labels=c('Chromosome\nSegragetion','Golgi vesicle\nTransport','Respiratory complex\nassembly'))+
  xlab("") +
  ylab("Sensitivity") +
  scale_fill_manual(values = sensor_colors) +
  theme_bw() +
  theme(axis.text.x = element_blank(), legend.title = element_blank())

@@

nw_img <- cowplot::ggdraw() +
  cowplot::draw_image(img, width = 1)
go_plots <- cowplot::plot_grid(
  sens_deg_comp + theme(legend.position = "none"),
  sens_sens_comp + theme(legend.position = "none"),
  cowplot::get_legend(sens_deg_comp), eff_deg_comp + theme(legend.position = "none"),
  eff_eff_comp + theme(legend.position = "none"),
  cowplot::get_legend(eff_deg_comp),
  ncol = 3, labels = c("B", "C", "", "D", "E", "")
)
combined <- cowplot::plot_grid(nw_img, go_plots, nrow = 2, rel_heights = c(0.4, 0.6), labels = c("A", ""))
ggsave('reports/figures/CSHL_plots_022621/sens_deg.png', plot=sens_deg_comp+theme(legend.position='none'),width=4,height=4)
ggsave('reports/figures/CSHL_plots_022621/sens_sens.png', plot=sens_sens_comp+theme(legend.position='none'),width=4,height=4)
ggsave("reports/figures/paper_figures_0202_pcc_only/fig6.png", plot = combined, width = 9, height = 12)
```

>>>>

```{r}
library(reticulate)
# use_python("/home/oma21/miniconda3/envs/enm/bin/python")
use_condaenv("enm")
setwd("../")
source("src/R/plot_density_prs.R")
figure_path = 'reports/figures/0404_paperfigure_sensors/'
```

@@

```{r}
library(tidyverse)
library(glue)
library(cowplot)
library(ggpubr)
library(ggsignif)

@@

# Network plot only sensors
```{python}
from matplotlib.lines import Line2D
pos = e_pcc.graph_gc.nodes('pos')
fig, ax = plt.subplots(figsize=(12,12))
legend_elements = [    ]
e_pcc.plot_network_spring(ax=ax,
                          node_size=1,
                          node_color='black',
 #                        node_size = [100 if i in sensors_pcc.orf_name.values or i in effector_pcc.orf_name.values else 1 for i in e_pcc.nodes],
                         #node_color = ['red' if i in sensors_pcc.orf_name.values else 'blue' if i in effector_pcc.orf_name.values else 'black' for i in e_pcc.nodes],
                         edge_color='black')
#                         node_shape=['^' if i in sensors_pcc.orf_name.values else 'v' if i in effector_pcc.orf_name.values else 'o' for i in e_pcc.nodes])
nx.draw_networkx_nodes(e_pcc.graph_gc, nodelist=sensors_pcc.orf_name.values, node_size=200, pos=pos,
                          node_color='black',
                          node_shape='^',edgecolors='black',
                          linewidths=1)
legend_elements.append(
    Line2D([0], [0], marker='^', color='black', label=f'Sensors (No GO enrichment)',
                          markerfacecolor=sensor_colors[0], markersize=12, linestyle="None")
)
for itr, i in enumerate(sensor_order):
    #print(i, effector_colors[itr])

    orf_names_to_plot = sensors_pcc.loc[sensors_pcc.go_group==i, 'orf_name'].tolist()
    nx.draw_networkx_nodes(e_pcc.graph_gc, nodelist=orf_names_to_plot, node_size=200, pos=pos,
                          node_color=sensor_colors[itr],
                          node_shape='^',edgecolors='black',
                          linewidths=1)
    legend_elements.append(
        Line2D([0], [0], marker='^', color='black', label=f'Sensors ({i})',
                              markerfacecolor=sensor_colors[itr], markersize=16, linestyle="None")
    )
nx.draw_networkx_edges(nx.induced_subgraph(e_pcc.graph_gc, sensors_pcc.orf_name.tolist()), ax=ax , pos=pos, edge_color='red', alpha=0.5)
ax.set_facecolor('white')
legend_elements.extend(
    [Line2D([0], [0], marker='o', color='black', label='Genes',
                              markerfacecolor='black', markersize=4, linestyle="None"),
#                    Line2D([0], [0], marker='o', color='black', label='Effectors',
#                               markerfacecolor='black', markersize=10, linestyle="None"),
#                    Line2D([0], [0], marker='^', color='black', label='Sensors',
#                               markerfacecolor='black', markersize=10, linestyle="None"),
                       Line2D([0], [0], marker='o', color='black', label= 'High functional similarity',
                              markerfacecolor='black', markersize=0, linestyle="-"),
                   Line2D([0], [0], marker='o', color='red', label= 'Sensor-Sensor edges',
                              markerfacecolor='#018571', markersize=0, linestyle="-")
])
lgd = ax.legend(handles=legend_elements, fontsize=22,loc='center left', bbox_to_anchor=(1.1, 0.5))
figure_path = r.figure_path
plt.savefig(f'{figure_path}//tmp_nwsens.png',bbox_inches='tight')
#plt.savefig('tmp_nw.png',bbox_inches='tight')
```

@@

eff_deg_comp <- ggplot(effector_pcc %>% right_join(py$e_pcc$df)%>% mutate(go_group = factor(replace_na(as.character(go_group),"Others")),go_group=fct_reorder(go_group, eff),go_group=fct_relevel(go_group,'Others',after=Inf)), 
                       aes(x = go_group, y = deg, fill = go_group)) +
  geom_boxplot(outlier.shape = NA) +
  scale_fill_manual(
    values = c(effector_colors,'black'),
    labels = c("Chromosome\nSegregetion", "Golgi vesicle\nTransport", "Respiratory complex\nassembly",'Non-effector genes')
  ) +
  xlab("") +
  ylab("Degree") +
  theme_bw() +
  geom_signif(
    comparisons = list(c("golgi", "chromatin"), c("golgi", "mito"), c("mito", "chromatin")),
    annotation = c("**", "***", "ns"),
    y_position = c(115, 120, 130)
  ) +
  theme(
       axis.text.y=element_text(size=10),
        axis.title.y=element_text(size=14), axis.text.x = element_blank(), legend.title = element_blank(), legend.text = element_text(margin = margin(t = 10, b = 10))) # , legend.spacing.y = unit(2,'in'))+
ggsave(glue('{figure_path}//tmp_eff_deg_nolegend.png'), plot = eff_deg_comp+theme(legend.position='none'),width=4,height=4)
ggsave(glue('{figure_path}//tmp_eff_deg_withlegend.png'), plot = eff_deg_comp,width=6,height=4)

eff_eff_comp <- ggplot(effector_pcc %>% mutate(go_group = fct_reorder(go_group, eff)) %>%
  mutate(eff_norm = eff / 5183), aes(x = go_group, y = eff_norm, fill = go_group)) +
  geom_boxplot() +
  # scale_x_discrete(labels=c('Chromosome\nSegregetion','Golgi vesicle\nTransport','Respiratory complex\nassembly'))+
  xlab("") +
  ggpubr::stat_compare_means(method = "kruskal.test") +
  scale_fill_manual(values = effector_colors) +
  ylab("Effectiveness") +
  theme_bw() +
  theme(
        axis.text.y=element_text(size=10),
        axis.title.y=element_text(size=14),axis.text.x = element_blank(), legend.title = element_blank())
ggsave(glue('{figure_path}//tmp_eff_eff.png'), plot = eff_eff_comp+theme(legend.position='none'),width=4,height=4)

sens_deg_comp <- ggplot(sensors_pcc %>% drop_na() %>% right_join(py$e_pcc$df)%>% mutate(go_group = factor(replace_na(as.character(go_group),"Non-sensor genes")),go_group=fct_reorder(go_group, sens),go_group=fct_relevel(go_group,'Non-sensor genes',after=Inf)), aes(x = go_group, y = deg, fill = go_group)) +
  geom_boxplot(
    outlier.shape=NA) +
  #    scale_x_discrete(labels=c('Chromosome\nSegregetion','Golgi vesicle\nTransport','Respiratory complex\nassembly'))+
  xlab("") +
  ylab("Degree") +
  scale_fill_manual(values = c(sensor_colors[1:6],'black')) +
  ggpubr::stat_compare_means(method = "kruskal.test", label.x.npc = .3) +
  theme_bw() +
  theme(
        axis.title.y=element_text(size=14),
        axis.text.y=element_text(size=10),
    axis.text.x = element_blank(), legend.title = element_blank(),
    legend.text = element_text(margin = margin(t = 10, b = 10))
  )+scale_y_log10()
  ggsave(glue('{figure_path}//sens_deg_withlegend.png'), plot=sens_deg_comp+theme(legend.position='bottom'),width=6,height=4)
ggsave(glue('{figure_path}//sens_deg.png'), plot=sens_deg_comp+theme(legend.position='none'),width=4,height=4)

@@

sens_sens_comp <- ggplot(sensors_pcc %>% drop_na() %>% mutate(go_group = fct_reorder(go_group, sens)) %>%
  mutate(sens_norm = sens / 5183), aes(x = go_group, y = sens_norm, fill = go_group)) +
  geom_boxplot() +
  geom_signif(
    comparisons = list(
      c("hexose metabolic\nprocess", "phenylalanine\ntransport"), c("tricarboxylic\nacid cycle", "phenylalanine\ntransport"),
      c("phenylalanine\ntransport", "protein folding")
    ),
    annotation = c("**", "**", "*"), y_position = c(0.007, 0.0075, 0.008)
  ) +
  #    scale_x_discrete(labels=c('Chromosome\nSegregetion','Golgi vesicle\nTransport','Respiratory complex\nassembly'))+
  xlab("") +
  ylab("Sensitivity") +
  scale_fill_manual(values = sensor_colors) +
  theme_bw() +
  theme(
        axis.title.y=element_text(size=14),
        axis.text.y=element_text(size=10),
        axis.text.x = element_blank(), legend.title = element_blank())
ggsave(glue('{figure_path}//sens_sens.png'), plot=sens_sens_comp+theme(legend.position='none'),width=4,height=4)

@@

nw_img <- cowplot::ggdraw() +
  cowplot::draw_image(img, width = 1)
go_plots <- cowplot::plot_grid(
  sens_deg_comp + theme(legend.position = "none"),
  sens_sens_comp + theme(legend.position = "none"),
  cowplot::get_legend(sens_deg_comp), eff_deg_comp + theme(legend.position = "none"),
  eff_eff_comp + theme(legend.position = "none"),
  cowplot::get_legend(eff_deg_comp),
  ncol = 3, labels = c("B", "C", "", "D", "E", "")
)
combined <- cowplot::plot_grid(nw_img, go_plots, nrow = 2, rel_heights = c(0.4, 0.6), labels = c("A", ""))
ggsave(glue('{figure_path}//sens_deg.png'), plot=sens_deg_comp+theme(legend.position='none'),width=4,height=4)
ggsave(glue('{figure_path}//sens_sens.png'), plot=sens_sens_comp+theme(legend.position='none'),width=4,height=4)
#ggsave("reports/figures/paper_figures_0202_pcc_only/fig6.png", plot = combined, width = 9, height = 12)
```
